\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-05-06 doc/paper.tex
document minimum and maximum scale restrictions

@@

OnlyLowEnergyFlexibleSUSY = False; (* default *)

PotentialLSPParticles = { Chi, Cha, Glu, Sv, Su, Sd, Se };
\end{lstlisting}
%
The variable \code{FSModelName} contains the name of the \fs model.

@@

Furthermore, the user has to specify the form of three model
constraints: low-scale, susy-scale and high-scale constraints.  In \fs
they are named as \code{LowScale}, \code{SUSYScale} and
\code{HighScale}.  For each constraint there is (i) a scale definition
(named after the constraint), (ii) an initial guess for the scale
(concatenation of the constraint name and \code{FirstGuess}) and (iii)
a list of parameter settings to be applied at the scale (concatenation
of the constraint name and \code{Input}).
%
\begin{itemize}
\item \emph{High-scale constraint:} The high-scale constraint is
  usuall the GUT-scale constraint, applied at the scale where the
  gauge couplings $g_1$ and $g_2$ unify.  The high-scale can be
  defined by an equation of the form \code{g1 == g2} or by fixed scale
  value.
\item \emph{Susy-scale constraint:} The susy-scale constraint is the
  constraint where \fs will impose the EWSB conditions and calculate
  the spectrum.  It is usually defined by
  $\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$.
\item \emph{Low-scale constraint:} The low-scale constraint is the
  constraint where the gauge couplings $g_1$, $g_2$, $g_3$ and the
  Yukawa couplings $y_f$ will be calculated from given Standard Model
  input $\alpha_{\text{e.m.}}(M_Z)$, $\alpha_{s}(M_Z)$, $m_f^\pole$,
  $M_Z^\pole$, $M_W^\pole$, see
  Sec.~\ref{sec:calculation-of-gauge-couplings}--\ref{sec:calculation-of-yukawa-couplings}.
  This should be done at the $Z$ mass scale $M_Z$.  Note that the
  gauge and Yukawa couplings are calculated automatically and
  therefore do not need to be specified in the \code{LowScaleInput}
  variable.
\end{itemize}
%
Note, that \fs GUT-normalizes all gauge couplings.  Thus, the
high-scale definition takes the simple form \code{g1 == g2}.  Another
consequence is that in the calculation of the VEVs $v_u$ and $v_d$
from $M_Z$ and $\tan\beta$ at the low-scale the GUT-normalization has
to be taken into account, see above.

@@

\fs can create the helper function \code{get_lsp()}, which finds the
lightest supersymmetric particle (LSP).  To let this function be
created by \fs, the model file variable \code{PotentialLSPParticles}
must be set to a list of SUSY particles which are potential LSPs.  In
the model file example above, the particles \code{Chi}, \code{Cha},
\code{Glu}, \code{Sv}, \code{Su}, \code{Sd}, \code{Se} (neutralino,
chargino, gluino, sneutrino, up-type squark, down-type squark,
selectron) are considered to be LSPs.

>>>>

HighScaleMinimum = 1.0 10^10; (* optional *)

HighScaleMaximum = 1.0 10^18; (* optional *)

@@

OnlyLowEnergyFlexibleSUSY = False; (* default *)
\end{lstlisting}
%
The variable \code{FSModelName} contains the name of the \fs model.

@@

Furthermore, the user has to specify the form of three model
constraints: low-scale, susy-scale and high-scale constraints.  In \fs
they are named as \code{LowScale}, \code{SUSYScale} and
\code{HighScale}.  For each constraint there is (i) a scale definition
(named after the constraint), (ii) an initial guess for the scale
(concatenation of the constraint name and \code{FirstGuess}) and (iii)
a list of parameter settings to be applied at the scale (concatenation
of the constraint name and \code{Input}).  Optional a minimum and a
maximum value for the scale can be given (concatenation of the
constraint name and \code{Minimum} or \code{Maximum}, respectively).
This avoids underflows or overflows of the scale value during the
iteration.  This is especially useful in models where the iteration is
very unstable and the value of the scale is very sensitive to the
model parameters.
%
\begin{itemize}
\item \emph{High-scale constraint:} The high-scale constraint is
  usuall the GUT-scale constraint, applied at the scale where the
  gauge couplings $g_1$ and $g_2$ unify.  The high-scale can be
  defined by an equation of the form \code{g1 == g2} or by fixed scale
  value.
\item \emph{Susy-scale constraint:} The susy-scale constraint is the
  constraint where \fs will impose the EWSB conditions and calculate
  the spectrum.  It is usually defined by
  $\sqrt{m_{\tilde{t}_1}m_{\tilde{t}_2}}$.
\item \emph{Low-scale constraint:} The low-scale constraint is the
  constraint where the gauge couplings $g_1$, $g_2$, $g_3$ and the
  Yukawa couplings $y_f$ will be calculated from given Standard Model
  input $\alpha_{\text{e.m.}}(M_Z)$, $\alpha_{s}(M_Z)$, $m_f^\pole$,
  $M_Z^\pole$, $M_W^\pole$, see
  Sec.~\ref{sec:calculation-of-gauge-couplings}--\ref{sec:calculation-of-yukawa-couplings}.
  This should be done at the $Z$ mass scale $M_Z$.  Note that the
  gauge and Yukawa couplings are calculated automatically and
  therefore do not need to be specified in the \code{LowScaleInput}
  variable.
\end{itemize}
%
Note, that \fs GUT-normalizes all gauge couplings.  Thus, the
high-scale definition takes the simple form \code{g1 == g2}.  Another
consequence is that in the calculation of the VEVs $v_u$ and $v_d$
from $M_Z$ and $\tan\beta$ at the low-scale the GUT-normalization has
to be taken into account, see above.

@@
